Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-14 doc/JFLA2022/paper.tex
more on book comparison

We believe that current Coq books can broadly be divided into two categories:
\begin{enumerate}
\item[a)] \emph{Executable textbooks} that are in effect large, well-commented Coq programs from which other representations of the material (HTML, PDF) are derived using tools.
\item[b)] \emph{Traditional textbooks} generated from documentation languages such as LaTeX that are accompanied by standalone Coq formalizations and/or code snippets.
\end{enumerate}

@@

>>>>

We believe that Coq books can broadly be divided into two categories:
\begin{enumerate}
\item[a)] \emph{Executable textbooks} that are in effect large, well-commented Coq programs from which other representations of the material (HTML, PDF) are derived using tools.
\item[b)] \emph{Traditional textbooks} generated from documentation languages such as LaTeX that are accompanied by standalone Coq formalizations and/or code snippets.
\end{enumerate}

Table~\ref{tbl:books} shows a categorization of the Coq books in English we are aware of.

@@

Several traditional books, such as Coq'Art~\cite{BC04}, used custom tools during their writing process to keep code snippets synchronized with Coq. However, once a book is published, the accompanying code generally takes on a life of its own~\cite{CoqArtCommunity} and may come to substantially diverge from the book.

We believe the \Hydras electronic book finds good tradeoffs between the advantages of executable books and traditional books.
